Internal models of type theory

### 2013-11-11 article-models-tt.tex
ok I did the evil thing; extension is now judgmentally associative

>>>>

\subsubsection{Extension is compatible with itself}
The inference rules asserting that extension is compatible with itself assert
that contexts are unstructured lists of type declarations. This rule is
unavoidable if we want that for a type $A$ in context $\Gamma$, a type
in context $A$ is the same thing as a type in context $\ctxext{\Gamma}{A}$.

\begin{align}
& \inference{\jtype{\Gamma}{A}\qquad\jtype{\ctxext{\Gamma}{A}}{P}}
  {\jctxeq{\ctxext{{\Gamma}{A}}{P}}{\ctxext{\Gamma}{{A}{P}}}}\\
& \inference{\jtype{\ctxext{\Gamma}{A}}{P}\qquad\jtype{\ctxext{{\Gamma}{A}}{P}}{Q}}
  {\jtypeeq{\Gamma}{\ctxext{{A}{P}}{Q}}{\ctxext{A}{{P}{Q}}}}
\end{align}
